A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-19 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
正文加首页图，改随机噪声实验

% \begin{figure}[t]
%   \centering
%   \includegraphics[width=0.48\textwidth]{images_imperceptible/UAP.pdf}
%   \caption{Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations except the mere addition operations.} 
%   \label{fig:UAP}
% \end{figure}

@@

In this paper, we make the first attempt in finding the universal perturbations that fool a state-of-the-art Siamese tracker, \ie, SiamFC++ \cite{SiamFC++}, in a targeted attack manner, which comes at virtually no cost in the online-tracking phase. Specifically, we aim to attack the trackers by adding a universal perturbation to the template image and adding a \textit{fake target}, \ie, a small universal adversarial patch, into the search image adhering to the predefined trajectory (as shown in Figure \ref{fig:1}), so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Our generated video-agnostic perturbations allow perturbing a novel video to come at no additional cost except the mere addition operations -- and not require gradient optimization or network inference. Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \uline{\cite{LaSOT}}, UAV123 \cite{UAV123}, \uline{VOT2016} \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019} benchmarks demonstrate the effectiveness and efficiency of our approach.

@@

%%%%%%%% 消融实验：高斯噪声 %%%%
\begin{table}[t]
  \centering
  \caption{Attack performance using the gaussian random noises. The mean value is set to zero. The standard deviation (std) is changed from 0.1 to 100.0. The noises are added to both the template and the search image, position and size is the same of original setting. The experiment is performed on GOT-Val.}
  \begin{tabular}{@{}rccccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{std} & \multirow{2}{*}[-2pt]{SSIM}& \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{3-6}
                             &                            & AO                & SR                & AO               & SR               \\ \midrule
  1.0                        & 0.98                       & 0.760             & 0.896             & 0.142            & 0.101            \\
  10.0                       & 0.38                       & 0.761             & 0.898             & 0.143            & 0.102            \\
  100.0                      & 0.01                       & 0.715             & 0.850             & 0.152            & 0.112            \\ \bottomrule        
  \end{tabular}
  \label{table:noise}
\end{table}
\uline{\textit{Ablation Study: Attack performance of the random noise} To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions. 
% 我们使用高斯噪声代替训练好的扰动来攻击SiamFC++\_GoogleNet。我们在GOT-Val上进行实验。
Specifically, we replace the trained perturbations with the gaussion random noise to attack SiamFC++\_GoogleNet. The mean value of the random noise is 0. The standard deviation is changed from 1.0 to 100.0. The experiment is performed on GOT-Val.
% 实验结果的分析
As shown in Table \ref{table:noise}, Gaussian noise cannot effectively attack the tracker even if the standard deviation is up to 100.
}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.48\textwidth]{images_imperceptible/UAP_small.pdf}
  \caption{Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations except the mere addition operations.} 
  \label{fig:UAP}
\end{figure}

@@

In this paper, we make the first attempt in finding the universal perturbations (Figure \ref{fig:UAP}) that fool a state-of-the-art Siamese tracker, \ie, SiamFC++ \cite{SiamFC++}, in a targeted attack manner, which comes at virtually no cost in the online-tracking phase. Specifically, we aim to attack the trackers by adding a universal perturbation to the template image and adding a \textit{fake target}, \ie, a small universal adversarial patch, into the search image adhering to the predefined trajectory (as shown in Figure \ref{fig:1}), so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Our generated video-agnostic perturbations allow perturbing a novel video to come at no additional cost except the mere addition operations -- and not require gradient optimization or network inference. Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \uline{\cite{LaSOT}}, UAV123 \cite{UAV123}, \uline{VOT2016} \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019} benchmarks demonstrate the effectiveness and efficiency of our approach.

@@

%%%%%%%% 消融实验：随机扰动 %%%%
\begin{table}[t]
  \centering
  \caption{Attack performance using random patterns.
  The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:noise}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Perturbations used to \\ perfrom attack \end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack}\\ \cmidrule{2-5}
                                                         & AO                                      & SR                               & AO                & SR                  \\ \midrule
  Trained Perturbations                                  & 0.153                                   & 0.123                            & 0.840             & 0.890               \\
  Similar Pattern                                         & 0.736                                   & 0.871                            & 0.153             & 0.118               \\
  Gaussian Noise                                         & 0.740                                   & 0.875                            & 0.144             & 0.101               \\ \bottomrule        
  \end{tabular}
\end{table}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.48\textwidth]{images_imperceptible/random_gaussian.pdf}
  \caption{Visualization of random patterns.}
  \label{fig:random}
\end{figure}
\uline{\textit{Ablation Study: Attack performance of random patterns} To illustrate the effectiveness of the proposed method, we add random patterns on the template and search regions (see Figure \ref{fig:random}). 
Specifically, we design two kinds of random patterns: (1) the random pattern similar to the trained perturbations, and (2) the random pattern generated using zero-mean Gaussian noise with standard deviation 50.0.
We replace the trained perturbations with the random random pattern to attack SiamFC++\_GoogleNet. The experiment is performed on GOT-Val.
As shown in Table \ref{table:noise}, random patterns cannot effectively attack the tracker.
}
